Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2012-12-06 docs/tex/draft.tex
Created comprehensive algorithm for tying all parts together

\subsection{Convex Hull Procedure on TMRFs}
In the previous section we showed how to find $X_{AB} = \argmin_X \left( \theta_A E_A(X) + \theta_B E_B(X)\right)$, for any convex combination with $\theta_A$ and $\theta_B$.In this section, we will put it all together to define a comprehensive algorithm that can be used for finding the entire pareto frontier for sequence design tasks.

>>>>

\subsection{Convex Hull Procedure on TMRFs}
In the previous section we showed how to find $X_{AB} = \argmin_X \left( \theta_A E_A(X) + \theta_B E_B(X)\right)$, for any convex combination with $\theta_A$ and $\theta_B$.In this section, we will put it all together in Algorithm~\ref{algo:pareto1} and Algorithm~\ref{algo:pareto2} to define a comprehensive algorithm that can be used for finding the entire pareto frontier for sequence design tasks.

\begin{algorithm}
\caption{Pareto-Optimal MultiState Protein Design} \label{algo:pareto1}
\begin{algorithmic}[1]
\Procedure{Pareto-Frontier}{$\phi,\psi,O^A,O^B$}\Comment{Find Pareto frontier}
	\State Initialize queue $Q \gets \emptyset$
	\State $X_A \gets$ \Call{CMRF-Decode}{$\phi,\psi,O^A$}  \Comment{$\argmin_X E_A(X)$}
	\State $X_B \gets$ \Call{CMRF-Decode}{$\phi,\psi,O^B$}  \Comment{$\argmin_X E_B(X)$}
	\State Enqueue $(X_A,X_B)$
	\State $C_H \gets \{X_A,X_B\}$
	\Repeat
		\State Dequeue from Q a pair $(X_1,X_2)$ and assert($E_A(X_1) < E_A(X_2)$)
		\State $m \gets \frac{E_B(X_1)-E_B(X_2)}{E_A(X_1)-E_A(X_2)}$
		\State $\theta_A \gets \frac{-m}{1-m}$
		\State $\theta_B \gets \frac{1}{1-m}$
		\State $X_{AB} \gets $\Call{TMRF-Decode}{$\phi,\psi,O^A,O^B,\theta_A,\theta_B$}
		\Statex \Comment{$\argmin_X \theta_A E_A(X) + \theta_B E_B(X)$}		
		\If{$X_{AB} \neq X_A$ and $X_{AB} \neq X_B$ }
			\State $C_H \gets C_H \cup \{X_{AB}\}$
			\State Enqueue $(X_A,X_{AB})$ and $(X_{AB},X_B)$
		\EndIf
	\Until{Q is empty}
	\State \Return $C_H$
\EndProcedure
\Statex 
\Procedure{CMRF-Decode}{$\phi,\psi,O^A$}\Comment{Max decode CMRF}
	\State Allocate $V[N][K]$ \Comment{N is length of seq,K is numAA }
	\State Allocate $X_A[N]$	
	\For{$k \gets 1,K$}
		\State $V[1][k] \gets \psi(\mathbf{O^A_1},X_1{=}k)\phi(X_1{=}k)$
	\EndFor	
	\For{$i \gets 1,N$}
		\For{$k \gets 1,K$}
			\State $V[i][k] \gets \phi(X_i{=}k)\psi(\mathbf{O^A_i},X_i{=}k) \max_{j}\{\psi(X_{i}{=}k,X_{i-1}{=}j)V(i-1,j)\}$
			\State $Ptr[i][k] \gets \argmax_{j}\{\psi(X_{i}{=}k,X_{i-1}{=}j)V(i-1,j)\} $
		\EndFor		
	\EndFor
	\Statex \Comment{Now retrieve the pointers}
	\State $X_A[N] \gets \argmax_{k}V[N][k]$ 
	\For{$i \gets N-1,1$}
		\State	$X_A[i] \gets Ptr[i+1][X_A[i+1]]$
	\EndFor
	\State \bf{return} $X_A$
\EndProcedure
\algstore{paretobreak}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Pareto continued} \label{algo:pareto2}
\begin{algorithmic}[1]
\algrestore{paretobreak}

\Procedure{TMRF-Decode}{$\phi,\psi,O^A,O^B,\theta_A,\theta_B$}\Comment{Max Decode TMRF}
	\State Allocate $V[N][K]$ \Comment{N is length of seq,K is numAA }
	\State Allocate $X_{AB}[N]$	
	\For{$k \gets 1,K$}
		\State $V[1][k] \gets \psi(\mathbf{O^A_1},X_1{=}k)^{\theta_A}\psi(\mathbf{O^B_1},X_1{=}k)^{\theta_B}\phi(X_1{=}k)$
	\EndFor	
	\For{$i \gets 1,N$}
		\For{$k \gets 1,K$}
			\State $V[i][k] \gets \phi(X_i{=}k)\psi(\mathbf{O^A_i},X_i{=}k)^{\theta_A}\psi(\mathbf{O^B_1},X_1{=}k)^{\theta_B}
    \max_{j}\{\psi(X_{i}{=}k,X_{i-1}{=}j)V(i-1,j)\}$
			\State $Ptr[i][k] \gets \argmax_{j}\{\psi(X_{i}{=}k,X_{i-1}{=}j)V(i-1,j)\} $
		\EndFor		
	\EndFor
	\Statex \Comment{Now retrieve the pointers}
	\State $X_{AB}[N] \gets \argmax_{k}V[N][k]$ 
	\For{$i \gets N-1,1$}
		\State	$X_{AB}[i] \gets Ptr[i+1][X_{AB}[i+1]]$
	\EndFor
	\State \bf{return} $X_{AB}$
\EndProcedure

\end{algorithmic}
\end{algorithm}
